Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-18 tex/paper1/paper1.tex
more edits to the paper

Model selection is implemented using the Akaike Information Criterion
(AIC) and the Bayesian Information Criterion (BIC)
\citep{2007MNRAS.377L..74L}.  The AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv -2 \ln L_{max} - 2k
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  The BIC is defined as
\begin{equation}\label{eqn:bic}
BIC \equiv -2 \ln L_{max} - k\ln N
\end{equation}
where $N$ is the number of data points used in the fit (in this case
$N=899$, the number of non-zero frequencies of the Fourier power
spectrum).  Model selection is guided by calculating $\delta AIC =
AIC_{1} - AIC_{2}$ and $\delta BIC = BIC_{1} - BIC_{2}$.  Positive
values of $\delta AIC, \delta BIC$ express a preference for model 2
over model 1.

@@

However, even this approach to identifying oscillatory power is not
quite complete, as it simply rejects the null hypothesis that the
\PS\ can be adequately explained by a \PL\ \PS.

Model comparison techniques similar to that described in Section
\ref{sec:anal} are required to prefer a model with oscillatory content
over one without. The difficulty in finding narrow-band features in
Fourier power spectra against a background \PL\ \PS\ has been
recognized by \cite{2010MNRAS.402..307V} in the study of XMM-Newton
observations of highly variable Seyfert 1 galaxies.
\cite{2010MNRAS.402..307V} presents a model fitting and comparison
technique that is directly applicable to the search for oscillatory
power in coronal time-series.

@@

@@

@@

Finally, the AIA instrument filter response must also be understood
and modeled in in order to understand which emission lines contribute
to the final observed image, and ultimately the \Fps\ for each
region.  The AIA filter response has been studied by
\cite{2010AA...521A..21O}

@@

We are grateful to the developers of SSWIDL
\citep{1998SoPh..182..497F}, SunPy \citep{mumford-proc-scipy-2013},
PyMC \citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}, matplotlib
\citep{Hunter:2007} and Scientific Python stack for providing data
preparation, manipulation, analysis and display packages.  This work
was supported by NASA award NNX13AE03G S01 funded through NASA ROSES
NNH12ZDA001N-SHP.

>>>>

Model selection is implemented using the Akaike Information Criterion
(AIC) and the Bayesian Information Criterion (BIC)
\citep{2007MNRAS.377L..74L, WICS:WICS199}.  The AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv -2 \ln L_{max} - 2k
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  The BIC is defined as
\begin{equation}\label{eqn:bic}
BIC \equiv -2 \ln L_{max} - k\ln N
\end{equation}
where $N$ is the number of data points used in the fit (in this case
$N=899$, the number of non-zero frequencies of the Fourier power
spectrum).  Model selection is guided by calculating $\delta AIC =
AIC_{1} - AIC_{2}$ and $\delta BIC = BIC_{1} - BIC_{2}$.  Positive
values of $\delta AIC, \delta BIC$ express a preference for model 2
over model 1.

@@

However, even this approach to identifying oscillatory power is not
quite complete, as it simply rejects the null hypothesis that the
\PS\ can be adequately explained by a \PL\ \PS.  Model comparison
techniques similar to that described in Section \ref{sec:anal} are
required to prefer a model with oscillatory content over one
without. The difficulty in finding narrow-band features in Fourier
power spectra against a background \PL\ \PS\ has been recognized by
\cite{2010MNRAS.402..307V} in the study of XMM-Newton observations of
highly variable Seyfert 1 galaxies.  \cite{2010MNRAS.402..307V}
presents a model fitting and comparison technique that is directly
applicable to the search for oscillatory power in coronal time-series.

@@

Another possible cause of the excess emission is the appearance of
low-temperature emission lines in the AIA passband.  Such lines are
more likely to be due to processes lower down in the solar atmosphere
where the amplitude of three and five minute oscillations is larger.
This is supported by three dimensional magnetohydrodynamic models of
the quiet Sun studied by \cite{2011ApJ...743...23M}.  It is shown that
lower temperature lines can be formed in quiet Sun areas that appear
in the AIA 171\AA\ and 193\AA\ wavebands. \cite{2011ApJ...743...23M}
find that the AIA 193\AA\ has more significant contributions from
non-dominant lines when compared to AIA 171\AA.  If this were the
case, then one would expect that the maximum of the ratio between
$G(\nu)/P_{1}(\nu)$ would be higher for the AIA 193\AA\ \PS\ than for
the AIA 171AA\ \PS, which is not obeserved.  However,
\cite{2011ApJ...743...23M} also note that their results are also quite
sensitive to the abundances used in their simulations, which may
explain the differences between their simulations and the observations
presented here.

@@

\cite{2011ApJ...743...23M} describe three-dimensional

@@

Finally, the AIA instrument filter response must also be understood
and modeled in in order to understand which emission lines contribute
to the final observed image, and ultimately the \Fps\ for each
region.

The AIA filter response has been studied by
\cite{2010AA...521A..21O}

@@

We are grateful to the developers of SSWIDL
\citep{1998SoPh..182..497F}, IPython \citep{ipython}, SunPy
\citep{mumford-proc-scipy-2013}, PyMC
\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}, matplotlib
\citep{Hunter:2007} and Scientific Python stack for providing data
preparation, manipulation, analysis and display packages.  This work
was supported by NASA award NNX13AE03G S01 funded through NASA ROSES
NNH12ZDA001N-SHP.
